Symmetric Implicit Surface Microstructures for Hierarchical Design

### 2023-09-19 manuscript/main.tex
sync

Just like the Fourier series, the resulting basis function in Equation \ref{eq:basis_function_actual} is orthonormal, i.e.
%
\begin{equation}
  \begin{split}
    \iiint_{\Omega} \phi_{\mathbf{f}}(\mathbf{x}) \overline{\phi_{\mathbf{g}}(\mathbf{x})} dV = 0 \\
    %
    \iiint_{\Omega} \phi_{\mathbf{f}}(\mathbf{x}) \overline{\phi_{\mathbf{f}}(\mathbf{x})} dV = 1 \\
  \end{split}
\end{equation}
%
for some arbitrary $\mathbf{f} \in \mathcal{T}$, $\mathbf{g} \in \mathcal{T}$, and $\mathbf{f} \neq \mathbf{g}$. The implicit surface $\Phi(\mathbf{x})$ may now be expressed in terms of a sum of the basis functions:
%
\begin{equation}
  \Phi(\mathbf{x}) = \sum\limits_{\mathbf{f} \in \mathcal{T}} c_{\mathbf{f}} \phi_{\mathbf{f}}(\mathbf{x})
\end{equation}
%
where $c_{\mathbf{f}}$ are the weight coefficients for each basis function.

@@

@@

\subsubsection{Higher Order Mesh Scaffolds}

>>>>

Just like the Fourier series, the resulting basis function in Equation \ref{eq:basis_function_actual} is orthonormal, i.e.
%
\begin{equation}
  \begin{split}
    \iiint_{\Omega} \phi_{\mathbf{f}}(\mathbf{x}) \overline{\phi_{\mathbf{g}}(\mathbf{x})} dV = 0 \\
    %
    \iiint_{\Omega} \phi_{\mathbf{f}}(\mathbf{x}) \overline{\phi_{\mathbf{f}}(\mathbf{x})} dV = 1 \\
  \end{split}
\end{equation}
%
for some arbitrary $\mathbf{f} \in \mathcal{T}$, $\mathbf{g} \in \mathcal{T}$, and $\mathbf{f} \neq \mathbf{g}$. The implicit surface $\Phi(\mathbf{x})$ may now be expressed in terms of a sum of the basis functions:
%
\begin{equation}
  \label{eq:symmetric_implicit_surface}
  \Phi(\mathbf{x}) = \sum\limits_{\mathbf{f} \in \mathcal{T}} c_{\mathbf{f}} \phi_{\mathbf{f}}(\mathbf{x})
\end{equation}
%
where $c_{\mathbf{f}}$ are the weight coefficients for each basis function.

@@

In addition to symmetry constraints, the implicit surface unit cell can be further constrained to intersect with its bounding polygon/polyhedron at a right angle. We postulate this is an important property to have in order to generate hierarchical structures with $C^1$ continuity in higher order meshes with $C^1$ continuity constraints applied to control points (see Section \ref{sec:higher_order_scaffolds}). To apply this face normal constraint, we first note that the outward normal vector of an implicit surface is given by its gradient:
%
\begin{equation}
  \mathbf{N}(\mathbf{x}) = \nabla \Phi(\mathbf{x})
\end{equation}
%
To constrain the implicit surface to intersect its bounding polygon/polyhedron at a right angle, we need its outward normal to be at a right angle to the outward normal $\mathbf{N}_p$ of the polygon/polyhedron face. Thus, the dot product between these two vectors must be zero when evaluated on the polygon/polyhedron faces:
%
\begin{equation}
  \label{eq:face_normal_constraint}
  \nabla \Phi(\mathbf{x}) \cdot \mathbf{N}_p \rvert \mathbf{x} \rightarrow \mathbf{x}_p = 0
\end{equation}
%
where $\mathbf{x}_p$ is a point on the bounding polygon/polyhedron face. Note that due to the symmetry constraint already imposed from our usage of symmetric basis functions, we only need to satisfy Equation \ref{eq:face_normal_constraint} on one face of the bounding polygon/polyhedron, as it will be automatically applied to the other faces. We can rewrite $\mathbf{x}_p$ as
%
\begin{equation}
  \label{eq:face_projection}
  \mathbf{x}_p = \mathbf{A} \mathbf{x} + \mathbf{b}
\end{equation}
%
where $\mathbf{A} : \mathbb{R}^{d \times d}$ is a projection matrix and $\mathbf{b} : \mathbb{R}^d $ is an offset term. Equation \ref{eq:face_projection} can be geometrically interpreted as projecting a point $\mathbf{x}$ onto the extended plane of the chosen face of the bounding polygon/polyhedron. Using Equation \ref{eq:basis_function_actual} and \ref{eq:symmetric_implicit_surface}, the gradient term can be written as:
%
\begin{equation}
  \begin{split}
    \nabla \Phi(\mathbf{x}) &= \sum\limits_{\mathbf{f} \in \mathcal{T}} c_{\mathbf{f}} \nabla \phi_{\mathbf{f}}(\mathbf{x}) \\
    %
    &= 2 \pi i \sum\limits_{\mathbf{f} \in \mathcal{T}} c_{\mathbf{f}} K_{\mathbf{f}} \sum\limits_{\mathbf{Q} \in \mathcal{S}} \mathbf{Q}^T \mathbf{f} e^{2 \pi i \mathbf{f}^T \mathbf{Q} \mathbf{x}}
  \end{split}
\end{equation}
%

@@

\subsubsection{Higher Order Mesh Scaffolds}
\label{sec:higher_order_scaffolds}
